Responses to reviewers' comments and list of modifications done\\ on paper SORO226\\ \LARGE{\textbf{Grounding the interaction: anchoring situated discourse in everyday human-robot interaction}}

### 2011-07-17 cover_letter.tex
Addressed question on 'restrictive information'

\subsection{``how does the system deal with restrictive information vs.
attributive information expressed by adjectives (e.g., in "the yellow banana is
big")?''}

>>>>

\subsection{``how does the system deal with restrictive information vs.
attributive information expressed by adjectives (e.g., in ``the yellow banana is
big")?''}

When sentences like ``the yellow banana is big" are processed, they are
recognized as statements to be added to the ontology because of the state verb ``to be''
({\sc Dialogs} maintains a list of such verbs).

The nominal group is first resolved as usual (``the yellow banana''), and a new statement
is then generated that describe the new feature to be added to the concept.

Please refer to the {\sc GenerateDescription} algorithm in appendix to see how the
new statements are created.
